---
title: "How Much Should We Trust Staggered Didderence-in-Diffirences Estimates?"
author: "Group 2"
date: "2023-08-29"
output: powerpoint_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
id <- rep(1:1000,each=36)
year <- rep(1980:2015,1000)

data <- data.frame(
  firm_id = id,
  year = year
)
View(data)

#トリートメントはランダムじゃなくて1~500 = 0, 501~1000 = 1でいいんじゃない
#1998年のトリートメントの列（0 or 1）を追加
#1998年以降かどうかの列を追加
#固定効果・時間効果をN(0, 0.5^2)で作る




```

## Slide with Plot

```{r pressure}
plot(pressure)
```

